
\documentclass{article}
\usepackage[english]{babel}
\usepackage[letterpaper, top=0.5in, right=0.5in, bottom=0.5in, left=0.5in]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{lmodern}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}
\usepackage{indentfirst}
\setlength\parindent{0pt}
\usepackage{csquotes}
\usepackage{setspace}
\usepackage[inline]{enumitem}
\pagestyle{empty}
\setlist[itemize]{noitemsep,topsep=2pt,label={\small\raisebox{1pt}{\textbullet}}}

\newcommand{\headingOne}[1]{
    \subsection*{#1} \hrule
    \vspace*{6pt}
}
\newcommand{\headingTwo}[2]{
    \vspace*{6pt}
    \textbf{#1 \hfill #2}
}
\newcommand{\headingThree}[2]{
    \vspace*{2pt}
    \textsl{#1 \hfill #2}
}

\newcommand{\headingList}[1]{\vspace*{5pt}\textbf{#1}}


\begin{document}


\section*{Gaurav Sett}

\textbf{Contact}
\begin{itemize*}[label=$|$]
    \item \href{mailto:gauravsett@icloud.com}{gauravsett@icloud.com}
    \item \href{https://linkedin.com/in/gauravsett}{linkedin.com/in/gauravsett}
    \item \href{https://gauravsett.com}{gauravsett.com}
\end{itemize*}


\headingOne{Education}


\headingTwo{RAND}{Washington, DC}

\headingThree{PhD in Policy Analysis — Pardee RAND Graduate School}{2024-09|}
\begin{itemize}
    \item Artificial Intelligence specialization.
    \item Technology and Security Policy Scholar.
    % \item Comittee: 
\end{itemize}


\headingTwo{Georgia Tech}{Atlanta, GA}

\headingThree{MS in Computer Science — College of Computing}{2023-01|2023-08}
\begin{itemize}
    \item Machine Learning specialization; 4.0 GPA.
\end{itemize}

\headingThree{BS in Computer Science — College of Computing}{2019-08|2022-12}
\begin{itemize}
    \item Artificial Intelligence and Human-Computer Interaction specializations; 3.9 GPA, Honors Program.
\end{itemize}



\headingOne{Employment}


\headingTwo{RAND}{Washington, DC}

\headingThree{Assistant Policy Researcher}{2024-09|}
\begin{itemize}
    \item Conducting research on standards and regulation for AI systems.
    \item Supporting requests from policymakers for technical expertise on AI governance.
\end{itemize}

\headingThree{Technology and Security Policy Fellow}{2023-11—2024-09}
% \begin{itemize}
% \end{itemize}


\headingTwo{Washington Post}{Washington, DC}

\headingThree{Data Science Intern}{2022-05|2022-08}
\begin{itemize}
    \item Deployed transformer language model to analyze breaking news for journalists and editors.
    % \item Created API to handle continuous collection, processing, and storage of articles using AWS ECS, Lambda, and S3
    % \item Visualized breaking news topics and API performance on dashboard for journalists using Datadog
\end{itemize}


\headingTwo{Federal Reserve Board}{Washington, DC}

\headingThree{Economics Research Intern}{2021-05|2021-08}
\begin{itemize}
    \item Built application regularly used by policymakers to analyze quarterly earnings calls.
    % \item Automated collection, processing, and storage of 200K documents; used parallelization to improve speed 8x with Dask
    % \item Presented to economists on NLP techniques such as word vectors and LDA topic modeling with interactive Django app
\end{itemize}


\headingTwo{Georgia Tech Research Institute}{Atlanta, GA}

\headingThree{Undergraduate Research Intern}{2020-05|2020-12}
\begin{itemize}
    \item Gathered data and analyzed political discourse about COVID-19 on social media platforms.
    % \item Analyzed the partisan differences in tweets about COVID-19 topics from members of Congress using SpaCy
    % \item Built GUI application enabling social scientists to collect and analyze Twitter API data using PyQT5
\end{itemize}


\headingOne{Research}

\headingTwo{RAND}{}

\headingThree{Publications}{}
\begin{itemize}
    \item Smith \& \textbf{Sett} (2024). Considerations for Dual-Use Foundation Models with Widely Available Weights. \textsl{RAND Expert Insights}.
    \item Elmgren, \textbf{Sett}, \& Smith (2024). Considerations on AI Model Red-Teaming and Standards. \textsl{RAND Expert Insights}.
\end{itemize}

\headingThree{Presentations}{}
\begin{itemize}
    \item \textbf{Sett} (2024). Responsible Capability Scaling. \textsl{Frontier Model Evaluation Science Day}, Washington, District of Columbia.
\end{itemize}

\headingTwo{Georgia Tech}{}

\headingThree{Publications}{}
\begin{itemize}
    \item Conklin, Bae, \textbf{Sett}, Hoffman, \& Biddle (2023). Report on the Conference on Ethicial and Responsible Design in the National AI Institute: A Summary of Challenges. \textsl{Forthcoming}.
\end{itemize}

\headingThree{Presentations}{}
\begin{itemize}
    \item Conklin \& \textbf{Sett} (2023). AI Safety, Governance, and Alignment Tutorial. \textsl{2023 IEEE International Symposium on Ethics in Engineering, Science, and Technology (ETHICS)}, West Lafayette, Indiana.
\end{itemize}


\headingOne{Leadership}


\headingTwo{AI Safety Initiative at Georgia Tech}{}

\headingThree{Founder, Executive Director}{2022-08|2023-10}
\begin{itemize}
    \item Founded group hosting events, seminars, bootcamps, and research projects in AI alignment and governance.
    \item Managed programs for over 100 students, leading team operations, and supporting career transitions.
    % \item Open Philanthropy University Organizer Fellowship: Awarded \$7,100 grant to support work as group organizer
    % \item Open Philanthropy Group Support Grant: Secured \$5,000 grant to support research and education programs
\end{itemize}


\headingTwo{Supervised Program for Alignment Research}{}

\headingThree{Co-Founder, Program Manager}{2023-07|2023-09}
\begin{itemize}
    \item Launched program facilitating AI safety research projects for 15 advisors and 80 students across universities.
    \item Recruited participants, managed applications, and organized 18 projects in alignment, engineering, and policy.
\end{itemize}


\headingOne{Teaching}


\headingTwo{Georgia Tech}{}

\headingThree{Graduate Teaching Assistant — Introduction to Cognitive Science}{Spring 2023}

\headingThree{Graduate Teaching Assistant — Introduction to Cognitive Science}{Summer 2023}


\headingOne{Skills}

\headingList{Machine Learning}
\begin{itemize*}[label=$|$]
    \item Python
    \item R
    \item SQL
    \item PyTorch
    \item TensorFlow
    \item HuggingFace
    \item SciKit-Learn
    \item Pandas
    \item NumPy
    \item Matplotlib
\end{itemize*}

\headingList{Software Engineering}
\begin{itemize*}[label=$|$]
    \item Java
    \item C
    \item JavaScript 
    \item HTML/CSS 
    \item Git
    \item APIs
    \item AWS
    \item React
    \item Django
    \item Agile
\end{itemize*}

\end{document}
